Causal Forest Approach for Site-specific Input Management via On-farm Precision Experimentation

### 2022-03-19 Codes/PrepareResults.rmd
minor fixes

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.title = element_blank()) +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))
```

@@

field_m_error_low <- 
  ggplot(field_cell_low_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c() +
    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
    ggtitle("(1) Low error") +
    theme_figure

@@

field_m_error_high <- 
  ggplot(field_cell_high_sf) +
    geom_sf(aes(fill = yield_error), size = 0) +
    scale_fill_viridis_c() +
    labs(fill = expression(paste( ~ epsilon, " (kg/ha)"))) +
    ggtitle("(1) High error") +
    theme_figure
```

@@

```{r}
# sim_no <- c(300, 600, 900)
# sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
    geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
    scale_shape_manual(values = c(21, 23, 25)) +
    ylim(NA, 95) +
    labs(y = " RMSE of EONR Estimation (kg/ha)") +
    labs(x = " RMSE of Yield Prediction (kg/ha)") +
    theme_dist +
    labs(fill="Simulation Round", shape="Method") +
    guides(fill = guide_legend(override.aes=list(shape=21))) +
    # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
    # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
    theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) +
    labs(fill="Simulation Round", shape="Method") 
```

@@

# === Preparation === #
table_optN_prep_low <-
  Simres_low%>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

@@

#/*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_low <-
  Simres_low %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

@@

```{r}
#/*--------------------------------*/
#' ## EONR estimation
#/*--------------------------------*/
Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))

# === Preparation === #
table_optN_prep_high <-
  Simres_high%>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

@@

#/*--------------------------------*/
#' ## Yield prediction
#/*--------------------------------*/ 
report_table_y_high <-
  Simres_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

>>>>

# --- MB function to N --- #
vis_MB_curve <-
  ggplot(res_y_dt[variable == "Yield"]) +
  geom_line(
    aes(x = N, y = value, group = factor(group))
  ) +
  # geom_point(data = sub_dt, aes(x = opt_N, y = value, alpha = "Yield at EONR"), color = "red", size = 1.5) +
  # geom_segment(data = sub_dt, aes(x = N, xend=N, y = value, yend=-Inf), linetype = "dashed") +
  scale_alpha_manual(
    name = NULL,
    values = 1,
    breaks = "Yield at EONR",
    guide = guide_legend(override.aes = list(
      linetype = 0,
      shape = 16,
      color = "red"
    ))
  ) +
  labs(y = "Yield (kg/ha)") +
  labs(x = "N (kg/ha)") +
  theme_dist +
  theme(legend.title = element_blank())
```

@@

field_m_error_low <-
  ggplot(field_cell_low_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
  ggtitle("(1) Low error") +
  theme_figure

@@

field_m_error_high <-
  ggplot(field_cell_high_sf) +
  geom_sf(aes(fill = yield_error), size = 0) +
  scale_fill_viridis_c() +
  labs(fill = expression(paste(~epsilon, " (kg/ha)"))) +
  ggtitle("(1) High error") +
  theme_figure
```

@@

```{r}
# sim_no <- c(300, 600, 900)
sim_no <- c(10, 20, 30)

vis_RMSE_y_eonr <-
  res_y_test %>%
  .[sim %in% sim_no & Method %in% c("RF", "BRF", "CNN") & Model == "aabbyytt"] %>%
  ggplot() +
  geom_point(aes(x = rmse_y, y = rmse_optN, shape = Method, fill = factor(sim)), size = 2) +
  scale_shape_manual(values = c(21, 23, 25)) +
  ylim(NA, 95) +
  labs(y = " RMSE of EONR Estimation (kg/ha)") +
  labs(x = " RMSE of Yield Prediction (kg/ha)") +
  theme_dist +
  labs(fill = "Simulation Round", shape = "Method") +
  guides(fill = guide_legend(override.aes = list(shape = 21))) +
  # guides(fill=guide_legend(nrow=2, byrow=TRUE)) +
  # guides(shape=guide_legend(nrow=2, byrow=TRUE)) +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  labs(fill = "Simulation Round", shape = "Method")
```

@@

# === Preparation === #
table_optN_prep_low <-
  Simres_low %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

@@

# /*--------------------------------*/
#' ## Yield prediction
# /*--------------------------------*/
report_table_y_low <-
  Simres_low %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

@@

```{r}
# /*--------------------------------*/
#' ## EONR estimation
# /*--------------------------------*/
Simres_high <- readRDS(here("Shared/Results/for_writing/forest_summry_bySim_high.rds"))

# === Preparation === #
table_optN_prep_high <-
  Simres_high %>%
  .[, .(
    rmse_optN = format(round(mean(rmse_optN), 1), nsmall = 1),
    pi_loss = format(round(mean(pi_loss), 2), nsmall = 2)
  ), by = .(type, Method, Model)] %>%
  dcast(type + Model ~ Method, value.var = c("rmse_optN", "pi_loss")) %>%
  .[, `:=`(
    blank1 = NA, blank2 = NA, blank3 = NA
  )] %>%
  .[, .(type, Model, blank1, rmse_optN_RF, pi_loss_RF, blank2, rmse_optN_BRF, pi_loss_BRF, blank3, rmse_optN_CF_base, pi_loss_CF_base)]

@@

# /*--------------------------------*/
#' ## Yield prediction
# /*--------------------------------*/
report_table_y_high <-
  Simres_high %>%
  .[type == "test" & Method %in% c("RF", "BRF")] %>%
  .[, .(rmse_y = mean(rmse_y)), by = .(Method, Model)] %>%
  .[, rmse_y := format(round(rmse_y, 1), nsmall = 1)] %>%
  dcast(Model ~ Method, value.var = "rmse_y") %>%
  .[, CF_base := "-"] %>%
  mutate(
    across(
      everything(),
      as.character
    )
  ) %>%
  flextable(.) %>%
  set_header_labels(values = list(
    Model = "Model",
    RF = "RF",
    BRF = "BRF",
    CF_base = "CF-base"
  )) %>%
  align(align = "center", part = "all") %>%
  align(j = 1, align = "left", part = "all") %>%
  #- change the borders just for consistency with other figures -#
  hline_bottom(part = "all") %>%
  hline_top(part = "header") %>%
  autofit()
```

### 2022-03-19 Writing/manuscript_cea.rmd
minor fixes

```{r vis-MB-curve, fig.cap = "Figure F.1: Examples of Mitscherlich-Baule yield response curve"}
vis_MB_curve
```

@@

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "Figure I.1: The Relationship between Yield and EONR Prediction Performances ((scenario: aabbyytt)"}
vis_RMSE_y_eonr
```

>>>>

```{r vis-MB-curve, fig.cap = "Examples of site-specific Mitscherlich-Baule yield response curves"}
vis_MB_curve
```

@@

```{r, vis-RMSE-y-eonr, fig.width=5, fig.height=5, fig.cap = "The Relationship between Yield and EONR Prediction Performances under the aabbyytt scenario"}
vis_RMSE_y_eonr
```
